Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-20 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Update to use hurricaneexposuredata package

```{r echo = FALSE, message = FALSE, warning = FALSE}
library(hurricaneexposure)
library(knitr)
library(ggplot2)
library(gridExtra)
library(dplyr)
```

>>>>

```{r echo = FALSE, message = FALSE, warning = FALSE}
library(hurricaneexposure)
# install hurricane exposure data package if you don't already have it
# library(devtools)
# install_github("geanders/hurricaneexposuredata")
library(hurricaneexposuredata)
library(knitr)
library(ggplot2)
library(gridExtra)
library(dplyr)
```
